Analysis : exp220 - 228 (Nov 2018, for J Neurophys draft 2018)

### 2018-11-17 resistingrhythm/analysis/paper_figures_v4.Rmd
Ongoing fig design for the paper

    # Add metadata
    df$osc_code <- rep(o_c, nrow(df))
    df$osc_rate <- rep(o_r, nrow(df))
    df$stim_code <- rep(s_c, nrow(df))
    df$synapse <- rep("Excitatory", nrow(df))
    results224 <- rbind(results224, df)
  }
}

@@

    # Add metadata
    df$osc_code <- rep(o_c, nrow(df))
    df$osc_rate <- rep(o_r, nrow(df))
    df$synapse <- rep("Excitatory", nrow(df))
    df$stim_code <- rep(s_c, nrow(df))

@@

    # Add metadata
    df$osc_code <- rep(o_c, nrow(df))
    df$osc_rate <- rep(o_r, nrow(df))
    df$stim_code <- rep(s_c, nrow(df))
    df$synapse <- rep("Excitatory", nrow(df))

@@

    # Add metadata
    df$osc_code <- rep(o_c, nrow(df))
    df$osc_rate <- rep(o_r, nrow(df))
    df$stim_code <- rep(s_c, nrow(df))
    df$synapse <- rep("Inhibitory", nrow(df))

@@

      # Add metadata
      df$osc_code <- rep(o_c, nrow(df))
      df$osc_rate <- rep(o_r, nrow(df))
      df$stim_code <- rep(s_c, nrow(df))
      df$Ca_target <- rep(ca, nrow(df))
      df$synapse <- rep("Excitatory", nrow(df))

@@

# Figure: Main results
```{r fig.height=2.25, fig.width=5.5}
# Kappa no H, E
bind_rows(results220, results222) %>%
  filter(osc_rate < 0.1 | osc_rate > 0.4) %>% 
  mutate(kappa_coord=replace(kappa_coord, rate_k < 1, NA)) %>% 
  group_by(synapse, osc_rate) %>% 
  mutate(M=mean(kappa_coord), SD=sd(kappa_coord)) %>% 
  ggplot(mapping=aes(x=osc_rate, y=M, group=osc_rate, color=synapse)) +
    geom_point(size=0.8) +
    geom_errorbar(mapping=aes(x=osc_rate, ymin=M - SD, ymax=M + SD, color=synapse),
                  width=.15, size=0.2) +
    scale_color_manual(values=c("black", "grey")) +
    lims(y=c(0.0, 0.2)) +
    labs(title="d.", y="Kappa", x="Osc. rate (Hz)") +
    theme_classic() +
    theme(plot.title = element_text(hjust = -.3, size=18, face="bold"),
          legend.position="none") -> p1

# Kappa with H, E
bind_rows(results221, results223) %>% 
  filter(osc_rate < 0.1 | osc_rate > 0.4) %>% 
  mutate(kappa_coord=replace(kappa_coord, rate_k < 1, NA)) %>%
  group_by(synapse, osc_rate) %>% 
  mutate(M=mean(kappa_coord), SD=sd(kappa_coord)) %>% 
  ggplot(mapping=aes(x=osc_rate, y=M, group=osc_rate, color=synapse)) +
    geom_point(size=0.8) +
    geom_errorbar(mapping=aes(x=osc_rate, ymin=M - SD, ymax=M + SD, color=synapse),
                  width=.15, size=0.2) +
    scale_color_manual(values=c("black", "grey")) +
    lims(y=c(0.0, 0.2)) +
    labs(title="e.", y="Kappa", x="Osc. rate (Hz)") +
    theme_classic() +
    theme(plot.title = element_text(hjust = -.3, size=18, face="bold"),
          legend.position="none") -> p2

# Rate no H, E
bind_rows(results220, results222) %>% 
  filter(osc_rate < 0.1 | osc_rate > 0.4) %>% 
  mutate(kappa_coord=replace(kappa_coord, rate_k < 1, NA)) %>% 
  group_by(synapse, osc_rate) %>% 
  mutate(M=mean(rate_k), SD=sd(rate_k)) %>% 
  ggplot(mapping=aes(x=osc_rate, y=M, group=osc_rate, color=synapse)) +
  geom_point(size=0.8) +
  geom_errorbar(mapping=aes(x=osc_rate, ymin=M - SD, ymax=M + SD, color=synapse),
                width=.15, size=0.2) +
  scale_color_manual(values=c("black", "grey")) +
  labs(title="a.", y="Pop. rate (Hz)", x="Osc. rate (Hz)") +
  lims(y=c(0.0, 180.0)) +
  guides(fill = guide_legend(override.aes = list(shape = 15, size = 7, alpha=0.8))) +
  theme_classic() +
  theme(plot.title = element_text(hjust = -.3, size=18, face="bold"),
        legend.position="none") -> p3

# -
# Rate, with H, E
bind_rows(results221, results223) %>% 
  filter(osc_rate < 0.1 | osc_rate > 0.4) %>% 
  mutate(kappa_coord=replace(kappa_coord, rate_k < 1, NA)) %>%
  group_by(synapse, osc_rate) %>% 
  mutate(M=mean(rate_k), SD=sd(rate_k)) %>% 
  ggplot(mapping=aes(x=osc_rate, y=M, group=osc_rate, color=synapse)) +
  geom_point(size=0.8) +
  geom_errorbar(mapping=aes(x=osc_rate, ymin=M - SD, ymax=M + SD, color=synapse), 
                width=.15, size=0.2) +
  scale_color_manual(values=c("black", "grey")) +
  labs(title="b.", y="Pop. rate (Hz)", x="Osc. rate (Hz)") +
  lims(y=c(0.0, 180.0)) +
  theme_classic() +
  theme(
    legend.position = c(-.6, -0.2),
    legend.background = element_rect(colour ="black"),
    legend.key.size = unit(.5, "cm"),
    legend.title=element_blank(),
    plot.title = element_text(hjust = -.3, size=18, face="bold")) -> p4

# --------------------------------------------------------
bind_rows(results224, results227)  %>% 
  filter(osc_rate < 0.1 | osc_rate > 0.4) %>% 
  mutate(kappa_coord=replace(kappa_coord, rate_k < 1, NA)) %>%
  group_by(synapse, osc_rate) %>% 
  mutate(M=mean(kappa_coord), SD=sd(kappa_coord)) %>% 
  ggplot(mapping=aes(x=osc_rate, y=M, group=osc_rate, color=synapse)) +
    geom_point(size=0.8) +
    geom_errorbar(mapping=aes(x=osc_rate, ymin=M - SD, ymax=M + SD, color=synapse), 
                width=.15, size=0.2) +
    scale_color_manual(values=c("darkgoldenrod3", "goldenrod1")) +
    lims(y=c(0.0, 0.2)) +
    labs(title="f.", y="Kappa", x="Osc. rate (Hz)") +
    theme_classic() +
    geom_hline(yintercept=0, size=0.2) +
    theme(plot.title = element_text(hjust = -.3, size=18, face="bold"),
          legend.position="none") -> p5

# -
bind_rows(results224, results227)  %>% 
  filter(osc_rate < 0.1 | osc_rate > 0.4) %>% 
  mutate(kappa_coord=replace(kappa_coord, rate_k < 1, NA)) %>%
  group_by(synapse, osc_rate) %>% 
  mutate(M=mean(rate_k), SD=sd(rate_k)) %>% 
  ggplot(mapping=aes(x=osc_rate, y=M, group=osc_rate, color=synapse)) +
    geom_point(size=0.8) +
    geom_errorbar(mapping=aes(x=osc_rate, ymin=M - SD, ymax=M + SD, color=synapse), 
                width=.15, size=0.2) +
    scale_color_manual(values=c("darkgoldenrod3", "goldenrod1")) +
    labs(title="c.", y="Pop. rate (Hz)", x="Osc. rate (Hz)") +
    lims(y=c(0.0, 180.0)) +
    theme_classic() +
  theme(
    legend.position = c(1.35, .5),
    legend.background = element_rect(colour ="black"),
    legend.key.size = unit(.5, "cm"),
    legend.title=element_blank(),
    plot.title = element_text(hjust = -.3, size=18, face="bold")) -> p6

# -
tmp3 <- results221
tmp3$osc_mode <- rep("Sustained", nrow(results221))
tmp4 <- results224
tmp4$osc_mode <- rep("Burst", nrow(results224))

bind_rows(tmp3, tmp4) %>% 
  filter(synapse=="Excitatory") %>% 
  ggplot(aes(x=osc_mode, y=rate_k, color=osc_mode)) +
  geom_point(size=-1, aes(fill=osc_mode)) +
  geom_boxplot(notch = TRUE, width=0.4,  outlier.size=0.05, outlier.alpha=0.5, show.legend=FALSE) +
  labs(title="g.", y="Pop. rate (Hz)", x="") +
  theme_classic() +
  scale_fill_manual(values=c("darkgoldenrod3", "black"), name="Oscillation") +
  scale_color_manual(values=c("darkgoldenrod3", "black"), name="Oscillation") +
  stat_compare_means(method="wilcox.test", label="p.signif", 
                     label.x=1.3, size=3, show.legend=FALSE) +
  lims(y=c(0.0, 180.0)) +
  guides(fill = guide_legend(override.aes = list(shape = 15, size = 7, alpha=0.8))) +
  theme(plot.title = element_text(hjust = -.1, size=18, face="bold"), 
          legend.position="none",
          axis.text.x = element_text(angle = 70, hjust = 1)) -> p7

# -
p8 <- textGrob("No homeostatsis")
p9 <- textGrob("Homeostatsis")
p10 <- textGrob("Coordination")
p11 <- textGrob("Excitability")

# -
layout_matrix <- rbind(
  c(NA, 8, 8, NA, 9, 9, 9, 9, NA),
  c(11, 3, 3, NA, 4, 4, 6, 6, NA),
  c(11, 3, 3, NA, 4, 4, 6, 6, NA),
  c(11, 3, 3, NA, 4, 4, 6, 6, NA),
  c(11, 3, 3, NA, 4, 4, 6, 6, 7),
  c(10, 1, 1, NA, 2, 2, 5, 5, 7), 
  c(10, 1, 1, NA, 2, 2, 5, 5, 7), 
  c(10, 1, 1, NA, 2, 2, 5, 5, 7), 
  c(10, 1, 1, NA, 2, 2, 5, 5, 7)
)
grid.arrange(p1, p2, p3, p4, p5, p6, p7, p8, p9, p10, p11, layout_matrix=layout_matrix)

# -
# png(file="fig2.png", bg="white", width=9.0, height=4.5, unit="in", res=300)
# plot(p)
# dev.off()
```

@@

# Figure: Kap v Err
```{r, fig.width=3.25, fig.height=1.1}
# -
results220 %>% 
  filter(osc_rate < 0.1 | osc_rate > 0.4) %>% 
  mutate(kappa_coord=replace(kappa_coord, rate_k < 1, NA)) %>%
  group_by(osc_rate) %>% 
  mutate(
    M_error=mean(abs_error), SD_error=sd(abs_error), 
    M_kappa=mean(kappa_coord), SD_kappa=sd(kappa_coord)) -> tmp1
tmp1$mode <- rep("No homeostatsis", nrow(tmp1))
results221 %>% 
  filter(osc_rate < 0.1 | osc_rate > 0.4) %>% 
  mutate(kappa_coord=replace(kappa_coord, rate_k < 1, NA)) %>%
  group_by(osc_rate) %>% 
  mutate(
    M_error=mean(abs_error), SD_error=sd(abs_error), 
    M_kappa=mean(kappa_coord), SD_kappa=sd(kappa_coord)) -> tmp2
tmp2$mode <- rep("Homeostatsis", nrow(tmp2))

bind_rows(tmp1, tmp2) %>% 
ggplot(mapping=aes(x=M_kappa, y=M_error, color=mode)) +
  geom_point(size=0.2) +
  geom_errorbar(mapping=aes(x=M_kappa, ymin=M_error - SD_error, ymax=M_error + SD_error),
                width=0.004, size=0.2) +
  geom_errorbarh(mapping=aes(y=M_error, xmin=M_kappa - SD_kappa, xmax=M_kappa + SD_kappa),
                 height=0.002, size=0.2) +
  scale_color_manual(values=c("black", "darkgrey")) +
  labs(title="a.", y="Log error (s)", x="Kappa") +
  lims(x=c(0.0, 0.25)) +
  scale_y_log10() + annotation_logticks() +
  theme_classic() + 
  theme(plot.title = element_text(hjust = -.3, size=18, face="bold"),
        legend.position = "none") -> p1

@@

bind_rows(tmp1, tmp2) %>% 
ggplot(mapping=aes(x=M_kappa, y=M_error, color=mode)) +
  geom_point(size=0.2) +
  geom_errorbar(mapping=aes(x=M_kappa, ymin=M_error - SD_error, ymax=M_error + SD_error),
                width=0.004, size=0.2) +
  geom_errorbarh(mapping=aes(y=M_error, xmin=M_kappa - SD_kappa, xmax=M_kappa + SD_kappa),
                 height=0.002, size=0.2) +
  scale_color_manual(values=c("black", "darkgrey")) +
  labs(title="b.", y="Log error (s)", x="Kappa") +
  lims(x=c(0.0, 0.25)) + annotation_logticks() +
  theme_classic() + 
  scale_y_log10() +
  theme(plot.title = element_text(hjust = -.3, size=18, face="bold"),
        legend.title=element_blank()) -> p2

# -
p3 <- textGrob("Sustained")
p4 <- textGrob("Burst", gp=gpar(col="darkgoldenrod3"))

# -
layout_matrix <- rbind(
  c(3, 3, 4, 4, NA),
  c(1, 1, 2, 2, 2),
  c(1, 1, 2, 2, 2),
  c(1, 1, 2, 2, 2),
  c(1, 1, 2, 2, 2)
)
grid.arrange(p1, p2, p3, p4, layout_matrix=layout_matrix)
```

# Figure: Calcium control
```{r, fig.width=2.4, fig.height=1.8}
# -
results228 %>% 
  filter(osc_rate < 0.1 | osc_rate > 0.4) %>% 
  mutate(kappa_coord=replace(kappa_coord, rate_k < 1, NA)) %>%
  group_by(osc_rate, Ca_target) %>% 
  summarise(M=mean(kappa_coord), SD=sd(kappa_coord)) -> tmp1

tmp1 %>% 
  ggplot(aes(x=osc_rate, y=M, color=factor(Ca_target, 
                                           levels = c(0.0026, 0.0028, 0.003, 0.0032, 0.0034)))) +
  geom_line(size=0.8) +
  geom_point(size=1.5) +
  geom_errorbar(aes(ymin=M - SD, ymax=M + SD), alpha=0.5, width=.1, size=0.4)  +
  labs(title="b.", y="Kappa", x="Osc. rate (Hz)") +
  scale_color_manual(
    values=c("plum1", "plum2", "black", "plum3", "plum4"), 
    guide=FALSE) +
  theme_classic() +
  theme(plot.title = element_text(hjust = -.5, size=18, face="bold")) -> p1

@@

tmp2 %>% 
ggplot(aes(x=osc_rate, y=M, color=factor(Ca_target, 
                                         levels = c(0.0026, 0.0028, 0.003, 0.0032, 0.0034)))) +
  geom_line(size=0.8) +
  geom_point(size=1.5) +
  geom_errorbar(aes(ymin=M - SD, ymax=M + SD), alpha=0.5, width=.1, size=0.4)  +
  labs(title="a.", y="Pop. rate (Hz)", x="Osc. rate (Hz)") +
  scale_color_manual(
    values=c("plum1", "plum2", "black", "plum3", "plum4"), 
    name="Target [Ca]\n(mmolar)") +
  theme_classic() +
  theme(
    plot.title = element_text(hjust = -.5, size=18, face="bold"),
    legend.position = c(1.35, -0.5),
    legend.background = element_rect(colour ="black"),
    legend.key.size = unit(.4, "cm")) -> p2

# -
p3 <- textGrob("Coordination")
p4 <- textGrob("Excitability")

# -
layout_matrix <- rbind(
  c(6, 6, 6, 6), 
  c(4, 2, 2, 5),
  c(4, 2, 2, 5),
  c(4, 2, 2, 5),
  c(4, 2, 2, 5),
  c(3, 1, 1, 5),
  c(3, 1, 1, 5),
  c(3, 1, 1, 5), 
  c(3, 1, 1, 5) 
)
p5 <- nullGrob()
p6 <- textGrob("Target Calcium")
grid.arrange(p1, p2, p3, p4, p5, p6, layout_matrix=layout_matrix)

# -
# png(file="fig5.png", bg="white", width=4.2, height=3.8, unit="in", res=300)
# plot(p)
# dev.off()

rm(p1, p2, p3, p4, p5, p6, tmp1, tmp2)
```

>>>>

    # Add metadata
    df$osc_code <- rep(o_c, nrow(df))
    df$osc_rate <- rep(o_r, nrow(df))
    df$stim_code <- rep(s_c, nrow(df))
    df$synapse <- rep("AMPA", nrow(df))
    results224 <- rbind(results224, df)
  }
}

@@

    # Add metadata
    df$osc_code <- rep(o_c, nrow(df))
    df$osc_rate <- rep(o_r, nrow(df))
    df$synapse <- rep("AMPA", nrow(df))
    df$stim_code <- rep(s_c, nrow(df))

@@

    # Add metadata
    df$osc_code <- rep(o_c, nrow(df))
    df$osc_rate <- rep(o_r, nrow(df))
    df$stim_code <- rep(s_c, nrow(df))
    df$synapse <- rep("AMPA", nrow(df))

@@

    # Add metadata
    df$osc_code <- rep(o_c, nrow(df))
    df$osc_rate <- rep(o_r, nrow(df))
    df$stim_code <- rep(s_c, nrow(df))
    df$synapse <- rep("GABA", nrow(df))

@@

      # Add metadata
      df$osc_code <- rep(o_c, nrow(df))
      df$osc_rate <- rep(o_r, nrow(df))
      df$stim_code <- rep(s_c, nrow(df))
      df$Ca_target <- rep(ca, nrow(df))
      df$synapse <- rep("AMPA", nrow(df))

@@

# Figure: Main results
```{r fig.height=2.25, fig.width=6}
# Kappa no H, E
bind_rows(results220, results222) %>%
  filter(osc_rate < 0.1 | osc_rate > 0.4) %>% 
  mutate(kappa_coord=replace(kappa_coord, rate_k < 1, NA)) %>% 
  group_by(synapse, osc_rate) %>% 
  mutate(M=mean(kappa_coord), SD=sd(kappa_coord)) %>% 
  ggplot(mapping=aes(x=osc_rate, y=M, group=osc_rate, color=synapse)) +
    geom_point(size=0.8) +
    geom_errorbar(mapping=aes(x=osc_rate, ymin=M - SD, ymax=M + SD, color=synapse),
                  width=.15, size=0.2) +
    scale_color_manual(values=c("black", "grey")) +
    lims(y=c(0.0, 0.2)) +
    labs(title="b.", y="Kappa", x="Osc. rate") +
    theme_classic2() +
    theme(plot.title = element_text(hjust = -.3, size=18, face="bold"),
          legend.position="none") -> p1

# Kappa with H, E
bind_rows(results221, results223) %>% 
  filter(osc_rate < 0.1 | osc_rate > 0.4) %>% 
  mutate(kappa_coord=replace(kappa_coord, rate_k < 1, NA)) %>%
  group_by(synapse, osc_rate) %>% 
  mutate(M=mean(kappa_coord), SD=sd(kappa_coord)) %>% 
  ggplot(mapping=aes(x=osc_rate, y=M, group=osc_rate, color=synapse)) +
    geom_point(size=0.8) +
    geom_errorbar(mapping=aes(x=osc_rate, ymin=M - SD, ymax=M + SD, color=synapse),
                  width=.15, size=0.2) +
    scale_color_manual(values=c("black", "grey")) +
    lims(y=c(0.0, 0.2)) +
    labs(title="d.", y="Kappa", x="Osc. rate") +
    theme_classic2() +
    theme(plot.title = element_text(hjust = -.3, size=18, face="bold"),
          legend.position="none") -> p2

# Rate no H, E
bind_rows(results220, results222) %>% 
  filter(osc_rate < 0.1 | osc_rate > 0.4) %>% 
  mutate(kappa_coord=replace(kappa_coord, rate_k < 1, NA)) %>% 
  group_by(synapse, osc_rate) %>% 
  mutate(M=mean(rate_k), SD=sd(rate_k)) %>% 
  ggplot(mapping=aes(x=osc_rate, y=M, group=osc_rate, color=synapse)) +
  geom_point(size=0.8) +
  geom_errorbar(mapping=aes(x=osc_rate, ymin=M - SD, ymax=M + SD, color=synapse),
                width=.15, size=0.2) +
  scale_color_manual(values=c("black", "grey")) +
  labs(title="a.", y="Pop. rate", x="Osc. rate") +
  lims(y=c(0.0, 180.0)) +
  guides(fill = guide_legend(override.aes = list(shape = 15, size = 7, alpha=0.8))) +
  theme_classic2() +
  theme(plot.title = element_text(hjust = -.3, size=18, face="bold"),
        legend.position="none") -> p3

# -
# Rate, with H, E
bind_rows(results221, results223) %>% 
  filter(osc_rate < 0.1 | osc_rate > 0.4) %>% 
  mutate(kappa_coord=replace(kappa_coord, rate_k < 1, NA)) %>%
  group_by(synapse, osc_rate) %>% 
  mutate(M=mean(rate_k), SD=sd(rate_k)) %>% 
  ggplot(mapping=aes(x=osc_rate, y=M, group=osc_rate, color=synapse)) +
  geom_point(size=0.8) +
  geom_errorbar(mapping=aes(x=osc_rate, ymin=M - SD, ymax=M + SD, color=synapse), 
                width=.15, size=0.2) +
  scale_color_manual(values=c("black", "grey"), name="Tonic") +
  labs(title="c.", y="Pop. rate", x="Osc. rate") +
  lims(y=c(0.0, 180.0)) +
  theme_classic2() +
  theme(
    legend.position = c(-.5, -0.2),
    legend.background = element_rect(colour ="black"),
    legend.key.size = unit(.5, "cm"),
    plot.title = element_text(hjust = -.3, size=18, face="bold")) -> p4

# --------------------------------------------------------
bind_rows(results224, results227)  %>% 
  filter(osc_rate < 0.1 | osc_rate > 0.4) %>% 
  mutate(kappa_coord=replace(kappa_coord, rate_k < 1, NA)) %>%
  group_by(synapse, osc_rate) %>% 
  mutate(M=mean(kappa_coord), SD=sd(kappa_coord)) %>% 
  ggplot(mapping=aes(x=osc_rate, y=M, group=osc_rate, color=synapse)) +
    geom_point(size=0.8) +
    geom_errorbar(mapping=aes(x=osc_rate, ymin=M - SD, ymax=M + SD, color=synapse), 
                width=.15, size=0.2) +
    scale_color_manual(values=c("darkgoldenrod3", "goldenrod1")) +
    lims(y=c(0.0, 0.2)) +
    labs(title="f.", y="Kappa", x="Osc. rate") +
    theme_classic2() +
    theme(plot.title = element_text(hjust = -.3, size=18, face="bold"),
          legend.position="none") -> p5

# -
bind_rows(results224, results227)  %>% 
  filter(osc_rate < 0.1 | osc_rate > 0.4) %>% 
  mutate(kappa_coord=replace(kappa_coord, rate_k < 1, NA)) %>%
  group_by(synapse, osc_rate) %>% 
  mutate(M=mean(rate_k), SD=sd(rate_k)) %>% 
  ggplot(mapping=aes(x=osc_rate, y=M, group=osc_rate, color=synapse)) +
    geom_point(size=0.8) +
    geom_errorbar(mapping=aes(x=osc_rate, ymin=M - SD, ymax=M + SD, color=synapse), 
                width=.15, size=0.2) +
    scale_color_manual(values=c("darkgoldenrod3", "goldenrod1"), name="Burst") +
    labs(title="e.", y="Pop. rate", x="Osc. rate") +
    lims(y=c(0.0, 180.0)) +
    theme_classic2() +
  theme(
    legend.position = c(1.35, .5),
    legend.title = element_text(colour = 'darkgoldenrod3'),
    legend.background = element_rect(colour ="black"),
    legend.key.size = unit(.5, "cm"),
    plot.title = element_text(hjust = -.3, size=18, face="bold")) -> p6

# -
tmp3 <- results221
tmp3$osc_mode <- rep("Tonic", nrow(tmp3))
tmp4 <- results224
tmp4$osc_mode <- rep("Burst", nrow(tmp4))

tmp5 <- results223
tmp5$osc_mode <- rep("Tonic", nrow(tmp5))
tmp6 <- results227
tmp6$osc_mode <- rep("Burst", nrow(tmp6))

bind_rows(tmp3, tmp4, tmp5, tmp6) %>% 
  # filter(synapse=="AMPA") %>% 
  ggplot(aes(x=osc_mode, y=rate_k, color=osc_mode)) +
  geom_point(size=-1, aes(fill=osc_mode)) +
  geom_boxplot(notch = TRUE, width=0.4,  outlier.size=0.05, outlier.alpha=0.5, show.legend=FALSE) +
  facet_grid(.~synapse) +
  labs(title="g.", y="Pop. rate", x="") +
  theme_classic2() +
  scale_fill_manual(values=c("black", "black"), name="Oscillation") +
  scale_color_manual(values=c("black", "black"), name="Oscillation") +
  stat_compare_means(method="wilcox.test", label="p.signif", 
                     label.x=1.3, size=3, show.legend=FALSE) +
  # lims(y=c(0.0, 180.0)) +
  guides(fill = guide_legend(override.aes = list(shape = 15, size = 7, alpha=0.8))) +
  theme(plot.title = element_text(hjust = -.1, size=18, face="bold"), 
          legend.position="none",
          strip.background = element_blank(),
          axis.text.x = element_text(angle = 70, hjust = 1)) -> p7

# -
p8 <- textGrob("No homeostatsis")
p9 <- textGrob("Homeostatsis")
p10 <- textGrob("Synchrony")
p11 <- textGrob("Excitability")

# -
layout_matrix <- rbind(
  c(NA, 8, 8, 8, NA, 9, 9, 9, 9, 9, 9, NA, NA),
  c(11, 3, 3, 3, NA, 4, 4, 4, 6, 6, 6, NA, NA),
  c(11, 3, 3, 3, NA, 4, 4, 4, 6, 6, 6, NA, NA),
  c(11, 3, 3, 3, NA, 4, 4, 4, 6, 6, 6, NA, NA),
  c(11, 3, 3, 3, NA, 4, 4, 4, 6, 6, 6, 7, 7),
  c(10, 1, 1, 1, NA, 2, 2, 2, 5, 5, 5, 7, 7), 
  c(10, 1, 1, 1, NA, 2, 2, 2, 5, 5, 5, 7, 7), 
  c(10, 1, 1, 1, NA, 2, 2, 2, 5, 5, 5, 7, 7), 
  c(10, 1, 1, 1, NA, 2, 2, 2, 5, 5, 5, 7, 7)
)
grid.arrange(p1, p2, p3, p4, p5, p6, p7, p8, p9, p10, p11, layout_matrix=layout_matrix)

# -
png(file="fig2.png", bg="white", width=12.0, height=4.5, unit="in", res=300)
grid.arrange(p1, p2, p3, p4, p5, p6, p7, p8, p9, p10, p11, layout_matrix=layout_matrix)
dev.off()
```

@@

# Figure: Kap v Err
```{r, fig.width=3, fig.height=1.1}
# -
results220 %>% 
  filter(osc_rate < 0.1 | osc_rate > 0.4) %>% 
  mutate(kappa_coord=replace(kappa_coord, rate_k < 1, NA)) %>%
  group_by(osc_rate) %>% 
  mutate(
    M_error=mean(abs_error), SD_error=sd(abs_error), 
    M_kappa=mean(kappa_coord), SD_kappa=sd(kappa_coord)) -> tmp1
tmp1$mode <- rep("No homeostatsis", nrow(tmp1))
results221 %>% 
  filter(osc_rate < 0.1 | osc_rate > 0.4) %>% 
  mutate(kappa_coord=replace(kappa_coord, rate_k < 1, NA)) %>%
  group_by(osc_rate) %>% 
  mutate(
    M_error=mean(abs_error), SD_error=sd(abs_error), 
    M_kappa=mean(kappa_coord), SD_kappa=sd(kappa_coord)) -> tmp2
tmp2$mode <- rep("Homeostatsis", nrow(tmp2))

bind_rows(tmp1, tmp2) %>% 
ggplot(mapping=aes(x=M_kappa, y=M_error, color=mode)) +
  geom_point(size=0.2) +
  geom_errorbar(mapping=aes(x=M_kappa, ymin=M_error - SD_error, ymax=M_error + SD_error),
                width=0.004, size=0.2) +
  geom_errorbarh(mapping=aes(y=M_error, xmin=M_kappa - SD_kappa, xmax=M_kappa + SD_kappa),
                 height=0.002, size=0.2) +
  scale_color_manual(values=c("black", "darkgrey")) +
  labs(title="a.", y="Log error (s)", x="Kappa") +
  lims(x=c(0.0, 0.25)) +
  scale_y_log10() + annotation_logticks() +
  theme_classic2() + 
  theme(plot.title = element_text(hjust = -.3, size=18, face="bold"),
        legend.position = "none") -> p1

@@

bind_rows(tmp1, tmp2) %>% 
ggplot(mapping=aes(x=M_kappa, y=M_error, color=mode)) +
  geom_point(size=0.2) +
  geom_errorbar(mapping=aes(x=M_kappa, ymin=M_error - SD_error, ymax=M_error + SD_error),
                width=0.004, size=0.2) +
  geom_errorbarh(mapping=aes(y=M_error, xmin=M_kappa - SD_kappa, xmax=M_kappa + SD_kappa),
                 height=0.002, size=0.2) +
  scale_color_manual(values=c("black", "darkgrey")) +
  labs(title="b.", y="Log error (s)", x="Kappa") +
  lims(x=c(0.0, 0.25)) + annotation_logticks() +
  theme_classic2() + 
  scale_y_log10() +
  theme(plot.title = element_text(hjust = -.3, size=18, face="bold"),
        legend.title=element_blank()) -> p2

# -
p3 <- textGrob("Tonic")
p4 <- textGrob("Burst", gp=gpar(col="darkgoldenrod3"))

# -
layout_matrix <- rbind(
  c(3, 3, 4, 4, NA),
  c(1, 1, 2, 2, 2),
  c(1, 1, 2, 2, 2),
  c(1, 1, 2, 2, 2),
  c(1, 1, 2, 2, 2)
)
grid.arrange(p1, p2, p3, p4, layout_matrix=layout_matrix)

png(file="fig3.png", bg="white", width=6, height=2.1, unit="in", res=300)
grid.arrange(p1, p2, p3, p4, layout_matrix=layout_matrix)
dev.off()
```

# Figure: Calcium control
```{r, fig.width=2.4, fig.height=1.6}
# -
results228 %>% 
  filter(osc_rate < 0.1 | osc_rate > 0.4) %>% 
  mutate(kappa_coord=replace(kappa_coord, rate_k < 1, NA)) %>%
  group_by(osc_rate, Ca_target) %>% 
  summarise(M=mean(kappa_coord), SD=sd(kappa_coord)) -> tmp1

tmp1 %>% 
  ggplot(aes(x=osc_rate, y=M, color=factor(Ca_target, 
                                           levels = c(0.0026, 0.0028, 0.003, 0.0032, 0.0034)))) +
  geom_line(size=0.8) +
  geom_point(size=1.5) +
  geom_errorbar(aes(ymin=M - SD, ymax=M + SD), alpha=0.5, width=.1, size=0.4)  +
  labs(title="b.", y="Kappa", x="Osc. rate") +
  scale_color_manual(
    values=c("plum1", "plum2", "black", "plum3", "plum4"), 
    guide=FALSE) +
  theme_classic2() +
  theme(plot.title = element_text(hjust = -.5, size=18, face="bold")) -> p1

@@

tmp2 %>% 
ggplot(aes(x=osc_rate, y=M, color=factor(Ca_target, 
                                         levels = c(0.0026, 0.0028, 0.003, 0.0032, 0.0034)))) +
  geom_line(size=0.8) +
  geom_point(size=1.5) +
  geom_errorbar(aes(ymin=M - SD, ymax=M + SD), alpha=0.5, width=.1, size=0.4)  +
  labs(title="a.", y="Pop. rate", x="Osc. rate") +
  scale_color_manual(
    values=c("plum1", "plum2", "black", "plum3", "plum4"), 
    name="Target [Ca]\n(mmolar)") +
  theme_classic2() +
  theme(
    plot.title = element_text(hjust = -.5, size=18, face="bold"),
    legend.position = c(1.35, -0.5),
    legend.background = element_rect(colour ="black"),
    legend.key.size = unit(.4, "cm")) -> p2

# -
p3 <- textGrob("Synchrony")
p4 <- textGrob("Excitability")

# -
layout_matrix <- rbind(
  c(4, 2, 2, 5),
  c(4, 2, 2, 5),
  c(4, 2, 2, 5),
  c(4, 2, 2, 5),
  c(3, 1, 1, 5),
  c(3, 1, 1, 5),
  c(3, 1, 1, 5), 
  c(3, 1, 1, 5) 
)
p5 <- nullGrob()
grid.arrange(p1, p2, p3, p4, p5, layout_matrix=layout_matrix)

png(file="fig4.png", bg="white", width=4.8, height=3.2, unit="in", res=300)
grid.arrange(p1, p2, p3, p4, p5, layout_matrix=layout_matrix)
dev.off()
```
